A Simple Model of Energy Transition Under a Carbon Budget

### 2015-04-27 DraftApril2715.tex
draft done except biblio and table vals

\paragraph{} However the most important sensitivity of the model is to the speed of clean capital cost reductions. Shown below in figure \ref{fig:costVsFl} are the optimal cost solutions to simulations run with different cost reduction speeds. A higher value on the x-axis means that the speed of transition is faster. Examples of the range of transmission profiles can be found above in figure \ref{fig:FlScaleScenarios}. For slow transitions, the model is extremely sensitive to improvements in cost reductions. As the speed of transition increases, the model becomes less sensitive to improvements, presumably because we reach the minimum cost per kilowatt-hour quickly.

@@

\paragraph{} A natural extension to this model would be endogenizing the cost of clean capital using a learning by doing approach.

@@

\paragraph{} Uncertainty

>>>>

@@

@@

\paragraph{} However the most important sensitivity of the model is to the speed of clean capital cost reductions. Shown below in figure \ref{fig:costVsFl} are the optimal cost solutions to simulations run with different cost reduction speeds. A higher value on the x-axis means that the speed of transition is faster. Examples of the range of transmission profiles can be found above in figure \ref{fig:FlScaleScenarios}. For slow transitions, the model is extremely sensitive to improvements in cost reductions. As the speed of transition increases, the model becomes less sensitive to improvements, presumably because we reach the minimum cost per kilowatt-hour quickly. A natural extension to this model would be endogenizing the cost of clean capital using a learning by doing approach. Alternatively, future work could include modeling this problem with uncertainty in the future distribution of cost reductions. Currently the model has perfect foresight, which may lead to over-investment in renewable technology early in the simulation as planners know that the cost effectiveness will increase in the future. With uncertainty in the cost of clean capital, we would better reflect the current challenges facing the clean energy transition
